Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/evalrelate.tex
some minor
abstract and other minor fixes

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traverse this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

\section{Evaluation}
We implemented our approach in a tool in Go programming language. We evaluated our tool by verifying correctness of pseudo-two-phase commit of figure \ref{lst:2pc} and example program of figure \ref{fig:exampleprog}. Our tool was able to infer the expected invariants in both of these programs. Also, different components of our tool such as program slicer, instrumenter and log merger have been tested in isolation to ensure correctness of the prototype. It is worth mentioning, that our prototype currently only handles scalar variables but extending it to handle structs is only an extra engineering effort. %We also do not perform interprocedural data and control flow analysis, so we always log all global variables and

>>>>

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traversed this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

\section{Evaluation}
We implemented our approach in a tool in Go programming language. We evaluated our tool by verifying correctness of pseudo-two-phase commit of figure \ref{lst:2pc} and example program of figure \ref{fig:exampleprog}. Our tool was able to infer the expected invariants in both of these programs. Also, different components of our tool such as program slicer, instrumenter and log merger have been tested in isolation to ensure correctness of the prototype. It is worth mentioning, that our prototype currently only handles scalar variables but extending it to handle structs is only an extra engineering effort. The source code for our analysis and the experimental data are available online\cite{distproject} as open source software.

 %We also do not perform interprocedural data and control flow analysis, so we always log all global variables and

### 2015-05-01 Doc/introback.tex
abstract and other minor fixes

\section{Abstract}
\section{Introduction}

@@

Invariants are properties that should hold in certain points in a program. Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is an open problem.To infer invariants in a distributed system we should have global snapshots (log of variables) of the system. However, not every snapshot of the system is a valid one. Mandy and Lamport introduced the notion of cut and consistent cut as snapshot and valid snapshots of a system. In \cite{mattern1989virtual}, Mattern proposed an algorithm to find consistent cuts. We used vector clocks \cite{vectorclock} to partially order snapshots of the nodes in our system and form consistent cuts. The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes consists a significant portion of distributed state of that node. We use static data and control flow analysis to detect the distributed state of the system. To do so we computed the forward and backward slice of the program  \cite{programslice} from communication points in the program, such as receive and send functions, and determined list of variables whose values are affected by a receive function or can affect values that are sent by a send function. By doing so, we identified the variables that contribute to interactions between nodes, possibly affect values of variables in other nodes, hence form the distributed state of the program.

>>>>

\section{Abstract}

Inferred invariants can show specification of systems, act as documentation and help program comprehension. This is even more useful in a distributed system where the state is defined globally across nodes and errors are propogated across node boundaries. But defining invariants manually is a laborious task and not feasible for a typical software system. So we propose a technique for inferring likely invariants of distributed systems from run time execution. We use data flow and control flow analyses to identify what contributes to the distributed state of the system. Then we use executions of the program to get runtime values and then use Daikon to infer invariants between variables. To achieve this, we have implemented a program slicer for Go programs, an instrumentation framework and a program--trace analyzer in Go. For evaluating our tool, we have successfully inferred invariants in few distributed programs including the two-phase-commit algorithm.

\section{Introduction}

@@

Invariants are properties that should hold in certain points in a program. Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is an open problem.To infer invariants in a distributed system we should have global snapshots (log of variables) of the system. However, not every snapshot of the system is a valid one. Mandy and Lamport introduced the notion of cut and consistent cut as snapshot and valid snapshots of a system. In \cite{mattern1989virtual}, Mattern proposed an algorithm to find consistent cuts. We used vector clocks \cite{vectorclock} to partially order snapshots of the nodes in our system and form consistent cuts. The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes constitute a significant portion of distributed state of that node. We use static data flow and control flow analysis to identify the distributed state of the system. To do so we computed the forward and backward slices of the program  \cite{programslice} from communication points in the program, such as receive and send functions, and determined list of variables whose values are affected by a receive function or can affect values that are sent by a send function. By doing so, we identified the variables that contribute to interactions between nodes, possibly affect values of variables in other nodes, hence form the distributed state of the program.
